Assessing the potential of Jacobian-free Newton-Krylov methods for cell-centred finite volume solid mechanics

### 2024-09-28 article.tex
Updates to Sec 4.2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Paper outline:
%
%Intro
%- FV is of interest for CSM
%- Most methods use segregated algorithms, stemming from CFD algorithms
%- Extension to block-coupled Newton methods is not easy, in terms of derivation, and code refactoring (matrix storage, extended stencil, linear solver, etc.).
%- JFNK promises the performance of Newton methods, but without the need to form the full Jacobian. Define JFNK method. Hence, an existing segregated code can easily be adapted to use JFNK without major refactoring, albeit this process is made easier by the availability of open-source JFNK implementations.
%- this paper examines JFNK for linear and nonlinear FV CSM procedures, where the compact stencil approximate Jacobian is used for preconditioning.

Finite volume formulations for solid mechanics are heavily influenced by their fluid mechanics counterparts, favouring segregated implicit and fully explicit methods.
Segregated approaches, where the governing momentum equation is temporarily decomposed into scalar component equations, offer memory efficiency and simplicity of implementation, but the outer coupling Picard iterations often suffer from slow convergence.
Explicit formulations are straightforward to implement and offer superior robustness but are only efficient for high-speed dynamics, where the physics requires small time increments.
In contrast, the finite element community commonly employs Newton-Raphson-type solution algorithms, which necessitate repeated assembly of the Jacobian matrix and solution of the resulting block-coupled non-diagonally dominant linear system.
A disadvantage of traditional Newton-based approaches is that they typically require explicit formation and storage of the Jacobian matrix, which can be computationally expensive and memory-intensive.
A further disadvantage from a finite volume perspective is that extending existing code frameworks from segregated algorithms to a coupled Newton-Raphson-type approach is challenging in terms of the required assembly, storage, and solution of the resulting block-coupled system.
In addition, the derivation of the true Jacobian matrix is non-trivial.
Consequently, similar block-coupled solution finite volume methods are rare in the literature \citep{Das2011, Cardiff2016, Castrillo2024}.
The motivation of the current work is to seek (or exceed) the robustness and efficiency of block-coupled Newton-Raphons approaches in a way that can be easily incorporated into existing segregated solution frameworks.
To this end, the current article examines the efficacy of \emph{Jacobian-free} Newton-Krylov methods, where the quadratic convergence of Newton methods can potentially be achieved without deriving, assembling and storing the exact Jacobian.

@@

\paragraph{Case 3: Narrow T-section component under tension}
This case, proposed by \citet{Demirdzic1997a}, consists of a narrow engineering component with a T cross-section (Figure \ref{fig:narrowTmember}).
The case is 3-D, static, with linear elastic material behaviour.
Symmetry allows one-quarter of the geometry to be simulated.
A constant negative pressure of 1 MPa is applied to the lower surface, and the upper left surface is fully clamped.
The Young’s modulus is $E = 210$ GPa and Poisson’s ratio is $\nu = 0.3$.
A radius $5$ mm hole is located at the expected stress concentration.
%\begin{figure}[htbp]
%   \centering
%   \includegraphics[width=0.4\textwidth]{figures/narrowTmember-geometry.pdf} 
%   \caption{Inflation of an idealised ventricle case geometry, mesh and loading conditions}
%   \label{fig:narrowTmember}
%\end{figure}
\begin{figure}[htbp]
	\centering
	\subfigure[Case geometry (considered quarter geometry)]
	{
		\label{fig:narrowTmember_geometry}
   		\includegraphics[height=0.4\textwidth]{figures/narrowTmember-geometry} 
   	}
   	\qquad
	\subfigure[Mesh with 624 cells]
	{
		\label{fig:narrowTmember_mesh}
   		\includegraphics[height=0.4\textwidth]{figures/narrowTmember-mesh}  
   	}
	\caption{Narrow T-section component under tension: geometry and mesh}
	\label{fig:narrowTmember}
\end{figure}

@@

\paragraph{Case 4: Inflation of an idealised ventricle}
Inflation of an idealised ventricle (Figure \ref{fig:ventricle}) was proposed by \citet{Land2015} as a benchmark problem for cardiac mechanics software.
The case is 3-D, static, with finite hyperelastic strains.
The initial geometry is defined as a truncated ellipsoid:
\begin{eqnarray}
	x = r_s \sin(u) \cos(v), \quad
	y = r_s \sin(u) \sin(v), \quad
	z = r_l \cos(u)
\end{eqnarray}
where on the inner (endocardial) surface $r_s =7$ mm, $r_l = 17$ mm, $u \in \left[-\pi, -\arccos \left( \frac{5}{17} \right) \right]$ and $v \in \left[-\pi, \pi \right]$, while on the outer (epicardial) surface $r_s =10$ mm, $r_l = 20$ mm, $u \in \left[-\pi, -\arccos \left( \frac{5}{20} \right) \right]$ and $v \in \left[-\pi, \pi \right]$.
The base plane $z = 5$ mm is implicitly defined by the ranges for $u$.
%Constitutive parameters: isotropic, 
The hyperelastic material behaviour is described by the transversely isotropic constitutive proposed by \citet{Guccione1995} law, where the parameters are $C = 10$ kPa, $b_f = b_t = b_{fs} = 1$.
The benchmark specifies an incompressible material; in the current work, incompressibility is enforced weakly using a penalty approach, where the bulk modulus parameter is chosen to be two orders of magnitude greater ($\kappa = 1000$ kPa) than the greatest shear modulus parameter.
The chosen parameters produce isotropic behaviour.
A pressure of 10 kPa is applied to the inner surface, and the base plane is fixed.
The geometry is meshed using a structured approach and is predominantly composed of hexahedra, with prism cells forming the apex.
The OpenFOAM utilities \texttt{blockMesh} and \texttt{extrudeMesh} are used to create the meshes.
Four successively refined meshes are examined: 1,620 (shown in Figure \ref{fig:ventricle}(a)), 12,960, 103,680, and 829,440 cells.
The case can be simulated as 2-D axisymmetric, but is simulated here using the full 3-D geometry.
%Figure \ref{fig:ventricle} shows the mesh with 1,620 cells (1,512 hexahedra and 108 prisms).
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.4\textwidth]{figures/ventricle} 
	\subfigure[Ventricle undeformed geometry, showing the mesh with 1,620 cells]
	{
		\includegraphics[height=0.46\textwidth]{figures/ventricle} 
	}
	\subfigure[Cross-section showing the equivalent (von Mises) stress distribution for the mesh with 829,440 cells]
	{
		\includegraphics[height=0.48\textwidth]{figures/ventricle_sigmaEq}
	}
   \caption{Idealised ventricle case}
   \label{fig:ventricle}
\end{figure}

@@

Figure \ref{fig:hronTurek-results} shows the velocity field in the fluid region and displacement magnitude in the solid region at $t = 4.42$ s, corresponding to a peak in the vertical displacement of the plate free-end oscillation.
The fluid is seen to accelerate as it passes the cylinder, with regular vortices being thrown off the plate, causing it to oscillate.
\begin{figure}[htbp]
   \centering
	   \includegraphics[width=\textwidth]{figures/hronTurek-results} 
%	\subfigure[Velocity field in the fluid region and displacement magnitude in the solid region at $t = 4.42$ s]
%	{
%	   \includegraphics[width=0.8\textwidth]{figures/hronTurek-results} 
%   	}
%	\subfigure[Vertical displacement of the end of the plate vs time]
%	{
%   		\includegraphics[width=0.3\textwidth]{figures/placeholder}  
%   	}
   \caption{Elastic plate behind a rigid cylinder case results at $t = 20$ s for the mesh with $20\,032$ cells in the fluid region and $2\,496$ in the solid region. The velocity magnitude is shown in the fluid region while the displacement magnitude is shown in the solid region.}
   \label{fig:hronTurek-results}
\end{figure}
The predicted mean, amplitude and frequency of the vertical and horizontal displacement of the end of the plate are compared with the results from \citet{Turek2006} in Table \ref{tab:hronTurekDisp}.
As directed in \citet{Turek2006}, the maximum and minimum values for the last period are used to calculate the mean and amplitude:
\begin{eqnarray}
	\text{mean} = \frac{1}{2}(\text{max} + \text{min}), \quad\quad
	\text{amplitude} = \frac{1}{2}(\text{max} - \text{min})
\end{eqnarray}
while the frequency is calculated as the inverse of the period.
\begin{table}[htb]
	\centering
		\begin{tabular}{lll}
			\hline
			Mesh (number of fluid and solid cells) & $u_x$ (in mm) & $u_y$ (in mm) \\
			\hline
			%  \hl{This data is taken as the average from 4-6 seconds: I am now running the case up to 20 seconds as per the benchmark}
%			1 ($1\,252$ + 156)  & $-0.1 \pm 0.01 \,[ 18.5 ]$ & $1.60 \pm 0.20 \,[ 5.5 ]$ \\
%			2 ($5\,008$ + 624)  & $-2.13 \pm 2.07 \,[ 11 ]$ & $2.00 \pm 28.84 \,[ 5.5 ]$ \\
%			3 ($20\,032$ + $2\,496$)  & $-2.62 \pm 2.46 \,[11]$ & $1.80 \pm 32.01 \,[ 5.5 ]$ \\
			% Data below is from the last cycle in the case run up to 20 s
			1 ($1\,252$ + 156)  & $ -0.1 \pm 0.001 \,[ 47.6 ]$ & $1.58 \pm 0.002 \,[ 5.88 ]$ \\
			2 ($5\,008$ + 624)  & $-2.16 \pm 2.00 \,[ 10.2 ]$ & $1.54 \pm 29.56 \,[ 5.6 ]$ \\
			3 ($20\,032$ + $2\,496$)  & $-2.51 \pm 2.37 \,[12.1]$ & $0.87 \pm 33.08 \,[ 5.6 ]$ \\
			\hline
			\citet{Turek2006} & $-2.69 \pm 2.53\,[10.9]$ & $1.48 \pm 34.38\,[5.3]$ \\
			\hline
		\end{tabular}
	\caption{Average predicted displacements (mean $\pm$ amplitude $[$frequency$]$) of the free end of the plate. Note that large-scale plate oscillations in mesh 1 (coarsest mesh) die out within the first 10 s. \hl{Hron-Turek say to use the last cycle, but surely taking the average of cycles would be better for benchmarking...} \hl{e.g. the average of the mesh 3 cycle is slightly lower than the rest} \hl{we could also report the average}}
		\label{tab:hronTurekDisp}
\end{table}

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Robustness and Resource Requirements}
\label{sec:resource_requirements}
%%--------------------------------------------------------------------------------------------------------------------%%
This section presents the time and memory requirements of the proposed Jacobian-free Newton-Krylov approach for the cases described above.
% where several mesh densities are examined.
Time and memory requirements from the classic segregated approach are given for comparison, along with the requirements from commercial finite element software Abaqus (version XXX): \hl{ask Dylan to create the Abaqus results when we are happy the paper will not change}.
The finite element approach uses a coupled solution algorithm and direct linear solver, where a Newton-Raphson method is used for resolving nonlinearities.
\hl{Take care when comparing times between different hardware}

Table \ref{tab:times_memory} lists the wall clock times (time according to a clock on the wall) and maximum memory usage according to the GNU time utility.
All clock times and memory usage were generated using \hl{hardware details} using one CPU core.
Times and maximum memory usage were recorded using the GNU time utility.
\hl{Give details of relevant numerical settings, e.g. linear solver, preconditioner, Rhie-Chow scaling, globalisation strategy if any}.
Multi-CPU-core parallelisation is examiend in Section \ref{sec:parallelisation}.
\begin{table}[htb]
	\centering
		\begin{tabular}{llll}
			\hline
			Case & Number of Cells & Time (in s) & Memory (in MB) \\
			\hline 
			Spherical cavity & 1,234 & 345 & 1,234  \\
			Spherical cavity & 12,345 & 345 & 1,234  \\
			Spherical cavity & 123,456 & 345 & 1,234  \\
			Case 2, etc & 123,456 & 345 & 1,234  \\
			Case 3, etc & 123,456 & 345 & 1,234  \\
			Case 4, etc & 123,456 & 345 & 1,234  \\
			\hline
		\end{tabular}
	\caption{Execution times and maximum memory usage \hl{speed-up column?}}
	\label{tab:times_memory}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Paper outline:
%
%Intro
%- FV is of interest for CSM
%- Most methods use segregated algorithms, stemming from CFD algorithms
%- Extension to block-coupled Newton methods is not easy, in terms of derivation, and code refactoring (matrix storage, extended stencil, linear solver, etc.).
%- JFNK promises the performance of Newton methods, but without the need to form the full Jacobian. Define JFNK method. Hence, an existing segregated code can easily be adapted to use JFNK without major refactoring, albeit this process is made easier by the availability of open-source JFNK implementations.
%- this paper examines JFNK for linear and nonlinear FV CSM procedures, where the compact stencil approximate Jacobian is used for preconditioning.
Finite volume formulations for solid mechanics are heavily influenced by their fluid mechanics counterparts, favouring segregated implicit and fully explicit methods.
Segregated approaches, where the governing momentum equation is temporarily decomposed into scalar component equations, offer memory efficiency and simplicity of implementation, but the outer coupling Picard iterations often suffer from slow convergence.
Explicit formulations are straightforward to implement and offer superior robustness but are only efficient for high-speed dynamics, where the physics requires small time increments.
In contrast, the finite element community commonly employs Newton-Raphson-type solution algorithms, which necessitate repeated assembly of the Jacobian matrix and solution of the resulting block-coupled non-diagonally dominant linear system.
A disadvantage of traditional Newton-based approaches is that they typically require explicit formation and storage of the Jacobian matrix, which can be computationally expensive and memory-intensive.
A further disadvantage from a finite volume perspective is that extending existing code frameworks from segregated algorithms to a coupled Newton-Raphson-type approach is challenging in terms of the required assembly, storage, and solution of the resulting block-coupled system.
In addition, the derivation of the true Jacobian matrix is non-trivial.
Consequently, similar block-coupled solution finite volume methods are rare in the literature \citep{Das2011, Cardiff2016, Castrillo2024}.
The motivation of the current work is to seek (or exceed) the robustness and efficiency of block-coupled Newton-Raphons approaches in a way that can be easily incorporated into existing segregated solution frameworks.
To this end, the current article examines the efficacy of \emph{Jacobian-free} Newton-Krylov methods, where the quadratic convergence of Newton methods can potentially be achieved without deriving, assembling and storing the exact Jacobian.

@@

\paragraph{Case 3: Narrow T-section component under tension}
This case, proposed by \citet{Demirdzic1997a}, consists of a narrow engineering component with a T cross-section (Figure \ref{fig:narrowTmember}).
The case is 3-D, static, with linear elastic material behaviour.
Symmetry allows one-quarter of the geometry to be simulated.
A constant negative pressure of 1 MPa is applied to the lower surface, and the upper left surface is fully clamped.
The Young’s modulus is $E = 210$ GPa, and Poisson’s ratio is $\nu = 0.3$.
A radius $5$ mm hole is located at the expected stress concentration.
%\begin{figure}[htbp]
%   \centering
%   \includegraphics[width=0.4\textwidth]{figures/narrowTmember-geometry.pdf} 
%   \caption{Inflation of an idealised ventricle case geometry, mesh and loading conditions}
%   \label{fig:narrowTmember}
%\end{figure}
\begin{figure}[htbp]
	\centering
	\subfigure[Case geometry (considered quarter geometry)]
	{
		\label{fig:narrowTmember_geometry}
   		\includegraphics[height=0.4\textwidth]{figures/narrowTmember-geometry} 
   	}
   	\qquad
	\subfigure[Mesh with 624 cells]
	{
		\label{fig:narrowTmember_mesh}
   		\includegraphics[height=0.4\textwidth]{figures/narrowTmember-mesh}  
   	}
	\caption{Narrow T-section component under tension: geometry and mesh}
	\label{fig:narrowTmember}
\end{figure}

@@

\paragraph{Case 4: Inflation of an idealised ventricle}
Inflation of an idealised ventricle (Figure \ref{fig:ventricle}) was proposed by \citet{Land2015} as a benchmark problem for cardiac mechanics software.
The case is 3-D, static, with finite hyperelastic strains.
The initial geometry is defined as a truncated ellipsoid:
\begin{eqnarray}
	x = r_s \sin(u) \cos(v), \quad
	y = r_s \sin(u) \sin(v), \quad
	z = r_l \cos(u)
\end{eqnarray}
where on the inner (endocardial) surface $r_s =7$ mm, $r_l = 17$ mm, $u \in \left[-\pi, -\arccos \left( \frac{5}{17} \right) \right]$ and $v \in \left[-\pi, \pi \right]$, while on the outer (epicardial) surface $r_s =10$ mm, $r_l = 20$ mm, $u \in \left[-\pi, -\arccos \left( \frac{5}{20} \right) \right]$ and $v \in \left[-\pi, \pi \right]$.
The base plane $z = 5$ mm is implicitly defined by the ranges for $u$.
%Constitutive parameters: isotropic, 
The hyperelastic material behaviour is described by the transversely isotropic constitutive proposed by \citet{Guccione1995} law, where the parameters are $C = 10$ kPa, $b_f = b_t = b_{fs} = 1$.
The benchmark specifies an incompressible material; in the current work, incompressibility is enforced weakly using a penalty approach, where the bulk modulus parameter is chosen to be two orders of magnitude greater ($\kappa = 1000$ kPa) than the greatest shear modulus parameter.
The chosen parameters produce isotropic behaviour.
A pressure of 10 kPa is applied to the inner surface, and the base plane is fixed.
The geometry is meshed using a structured approach and is predominantly composed of hexahedra, with prism cells forming the apex.
The OpenFOAM utilities \texttt{blockMesh} and \texttt{extrudeMesh} are used to create the meshes.
Four successively refined meshes are examined: $1\,620$ (shown in Figure \ref{fig:ventricle}(a)), $12\,960$, $103\,680$, and $829\,440$ cells.
The case can be simulated as 2-D axisymmetric but is simulated here using the full 3-D geometry.
%Figure \ref{fig:ventricle} shows the mesh with 1,620 cells (1,512 hexahedra and 108 prisms).
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.4\textwidth]{figures/ventricle} 
	\subfigure[Ventricle undeformed geometry, showing the mesh with 1,620 cells]
	{
		\includegraphics[height=0.46\textwidth]{figures/ventricle} 
	}
	\subfigure[Cross-section showing the equivalent (von Mises) stress distribution for the mesh with 829,440 cells]
	{
		\includegraphics[height=0.48\textwidth]{figures/ventricle_sigmaEq}
	}
   \caption{Idealised ventricle case}
   \label{fig:ventricle}
\end{figure}

@@

Figure \ref{fig:hronTurek-results} shows the velocity field in the fluid region and displacement magnitude in the solid region at $t = 4.42$ s, corresponding to a peak in the vertical displacement of the plate free-end oscillation.
The fluid is seen to accelerate as it passes the cylinder, with regular vortices being thrown off the plate, causing it to oscillate.
\begin{figure}[htbp]
   \centering
	   \includegraphics[width=\textwidth]{figures/hronTurek-results} 
%	\subfigure[Velocity field in the fluid region and displacement magnitude in the solid region at $t = 4.42$ s]
%	{
%	   \includegraphics[width=0.8\textwidth]{figures/hronTurek-results} 
%   	}
%	\subfigure[Vertical displacement of the end of the plate vs time]
%	{
%   		\includegraphics[width=0.3\textwidth]{figures/placeholder}  
%   	}
   \caption{Elastic plate behind a rigid cylinder case results at $t = 20$ s for the mesh with $20\,032$ cells in the fluid region and $2\,496$ in the solid region. The velocity magnitude is shown in the fluid region while the displacement magnitude is shown in the solid region.}
   \label{fig:hronTurek-results}
\end{figure}
The predicted mean, amplitude and frequency of the vertical and horizontal displacement of the end of the plate are compared with the results from \citet{Turek2006} in Table \ref{tab:hronTurekDisp}.
As directed in \citet{Turek2006}, the maximum and minimum values for the last period are used to calculate the mean and amplitude:
\begin{eqnarray}
	\text{mean} = \frac{1}{2}(\text{max} + \text{min}), \quad\quad
	\text{amplitude} = \frac{1}{2}(\text{max} - \text{min})
\end{eqnarray}
while the frequency is calculated as the inverse of the period.
\begin{table}[htb]
	\centering
		\begin{tabular}{lll}
			\hline
			Mesh (number of fluid and solid cells) & $u_x$ (in mm) & $u_y$ (in mm) \\
			\hline
			%  \hl{This data is taken as the average from 4-6 seconds: I am now running the case up to 20 seconds as per the benchmark}
%			1 ($1\,252$ + 156)  & $-0.1 \pm 0.01 \,[ 18.5 ]$ & $1.60 \pm 0.20 \,[ 5.5 ]$ \\
%			2 ($5\,008$ + 624)  & $-2.13 \pm 2.07 \,[ 11 ]$ & $2.00 \pm 28.84 \,[ 5.5 ]$ \\
%			3 ($20\,032$ + $2\,496$)  & $-2.62 \pm 2.46 \,[11]$ & $1.80 \pm 32.01 \,[ 5.5 ]$ \\
			% Data below is from the last cycle in the case run up to 20 s
			1 ($1\,252$ + 156)  & $ -0.1 \pm 0.001 \,[ 47.6 ]$ & $1.58 \pm 0.002 \,[ 5.88 ]$ \\
			2 ($5\,008$ + 624)  & $-2.16 \pm 2.00 \,[ 10.2 ]$ & $1.54 \pm 29.56 \,[ 5.6 ]$ \\
			3 ($20\,032$ + $2\,496$)  & $-2.51 \pm 2.37 \,[12.1]$ & $0.87 \pm 33.08 \,[ 5.6 ]$ \\
			\hline
			\citet{Turek2006} & $-2.69 \pm 2.53\,[10.9]$ & $1.48 \pm 34.38\,[5.3]$ \\
			\hline
		\end{tabular}
	\caption{Average predicted displacements (mean $\pm$ amplitude $[$frequency$]$) of the free end of the plate. Note that large-scale plate oscillations in mesh 1 (coarsest mesh) die out within the first 10 s.}
%	 \hl{Hron-Turek say to use the last cycle, but surely taking the average of cycles would be better for benchmarking...} \hl{e.g. the average of the mesh 3 cycle is slightly lower than the rest} \hl{we could also report the average}
		\label{tab:hronTurekDisp}
\end{table}

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Robustness and Resource Requirements}
\label{sec:resource_requirements}
%%--------------------------------------------------------------------------------------------------------------------%%
This section compares the robustness and resource requirements of the Jacobian-free Newton-Krylov and segregated approach on the cases presented in Section \ref{sec:accuracy}.
Specifically, cases where either approach diverges are examined, and the time and memory requirements are presented.
In some cases, time and memory requirements from finite element procedures for reference.
Time and memory requirements are implementation and hardware-specific; nonetheless, it is insightful to see the relative performances of the Jacobian-free Newton-Krylov and segregated approaches on the same hardware and within the same implementation framework.
% where several mesh densities are examined.
%Time and memory requirements from the classic segregated approach are given for comparison, along with the requirements from commercial finite element software Abaqus (version XXX): \hl{ask Dylan to create the Abaqus results when we are happy the paper will not change}.
%The finite element approach uses a coupled solution algorithm and direct linear solver, where a Newton-Raphson method is used for resolving nonlinearities.
%\hl{Take care when comparing times between different hardware}

Table \ref{tab:times_memory} lists the wall clock times (time according to a clock on the wall, rounded to the nearest second) and maximum memory usage according to the GNU time utility.
All clock times and memory usage were generated using a Mac Studio with an M2 Ultra CPU on one CPU core, where the code was built with the Clang compiler.
\hl{Present data for one hardware first, and give comparison after.}
Examination of multi-CPU-core parallelisation is left to Section \ref{sec:parallelisation}.
\begin{table}[htb]
	\centering
		\begin{tabular}{ll|ll|ll}
			\hline
			Case & Cell Count & \multicolumn{2}{c|}{JFNK} & \multicolumn{2}{c}{Segregated} \\
			     &            & Time (s) & Memory (MB) & Time (s) & Memory (MB) \\
			\hline 
			MMS & 384 & 0 & $78$ & X & Y \\
				& $4\,374$ & 0 & $86$ & X & Y \\
				& $41\,154$ & 1 & $195$ & X & Y \\
				&  $355\,914$ & 4 & $1\,063$ & X & Y \\
				& $2\,958\,234$ & 41 & $6\,724$ & X & Y \\
				& $24\,118\,074$ & 486 & $30\,606$ & X & Y \\
			\hline
			Elliptic & 45 & 0 & $72$ & X & Y \\
				& 472 & 0 & $78$ & X & Y \\
				& $4\,140$ & 1 & $153$ & X & Y \\
				& $34\,968$ & 7 & $754$ & X & Y \\
				& $287\,280$ & 95 & $3\,943$ & X & Y \\
				& $2\,438\,242$ & 988 & $21\,884$ & X & Y \\
			\hline
			T-member & 624& 0 & 84 & X & Y \\
				& $4\,992$ & 1 & 127 & X & Y \\
				& $39\,936$ & 10 & 557 & X & Y \\
				& $319\,488$ & 154 & $4\,024$ & X & Y \\
				& $2\,555\,904$ & $1\,751$ & $22\,814$ & X & Y \\
			\hline
			Ventricle & $1\,620$ & 54 & 133 & & \\
				& $12\,960$ & 576 & 553 & & \\
				& $103\,680$ & $8\,362$ & $3\,435$ & & \\
				& $829\,440$ & $150\,023$ & $11\,746$ & & \\
			\hline
		\end{tabular}
	\caption{Execution times and maximum memory usage for Jacobian-free Newton-Krylov (JFNK) and segregated methods. Resource requirements are shown for the following cases: manufactured solution (MMS), XX }
	\label{tab:times_memory}
\end{table}

\hl{Give details of relevant numerical settings, e.g. linear solver, preconditioner, Rhie-Chow scaling, globalisation strategy: where best to say this...}.
